Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-07-15 tmm.tex
final edit

There are generally two options to enable adaptive video streaming. The first option is called simulcast, where several independent bitstreams each with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth. Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option. The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, an extension of the H.264/AVC video coding standard \cite{SVCOverview}, which allows scalability of video bitrate and quality with only one single bitstream. In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs). These NALUs are separated into one base layer for basic video quality and multiple enhancement layers for video quality improvement. By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.

The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy. Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation. However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost. SVC streaming systems, on the contrary, do not have above shortcomings. Since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation. Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream. Therefore, we choose to adopt SVC in our adaptive video streaming framework. While the work of this paper partly applies to the simulcast system, it will mainly focus on the context of SVC video streaming system.

In the SVC adaptive video streaming system, there are two key problems that need to be addressed well. First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained. This is called the bitstream extraction problem. Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate. Second, when the bandwidth does change, it's necessary to make decisions about whether and how to adjust the bitrate or video quality. This problem is called quality control, which means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth. A good quality control algorithm should determine a suitable bitrate for current bandwidth condition, and keep the video quality both smooth and at a high level.

In this paper, an efficient adaptive video streaming system based on SVC is proposed with the above two problems better solved. Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the proposed system. The original DSS project is modified and SVC support is added to it, for the purpose of both research and application. Then novel algorithms for bitstream extraction and quality control are designed and implemented to achieve significant improvement in terms of user-perceived video quality. The contributions of our work can be summarized as follows:
\begin{itemize}
\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each packet according to its R-D impact, thus enables optimized bitstream extraction.
\item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
\end{itemize}

@@

Bitstream extraction is the operation of choosing a subset of data packets from a whole SVC bitstream to form a sub-stream. It makes the bitrate adjustable and is the prerequisite of an adaptive streaming system. Fig. \ref{fig:Bitstream-Extraction} illustrates the structure of an SVC stream and a possible way to extract a sub-stream from it. The data packets in the stream are divided into different layers. The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames, shown by the arrows on the top pointing from the referenced frame to the frame which is dependent on it. The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame, and packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction. For example, the dash line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.

@@

For a typical ``0-1 Knapsack Problem", the optimal solution can generally be found using the dynamic programming algorithm. However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the stream's data packets. First, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included. For example, in Fig. \ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame. Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets. Unless we discard a packet and calculate the distortion it causes for real, there is no way to exactly tell its value. In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem. All the effort is made to obtain a solution that is as good as possible.

@@

Quality control is the second problem we will address in this paper. The result of a quality control algorithm determines the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user. It should be noted that, the bitstream extraction is performed under constraint of that bitrate determined by quality control, and even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

@@

The following of this paper will present our solutions for the above problems in detail. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.

@@

Consider a video bitstream with 8-frame GOPs (Group of Pictures) shown in Fig. \ref{fig:GOP_Structure}. Base layer packets are colored black, and enhancement packets with the same color are allocated in one group. In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other. For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0). So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs. Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames. To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$. For the example in Fig. \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$. However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g. frame 0, 8, 16, etc.) packets. The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs. As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20). So key frame enhancement packets within the same quality layer (e.g. packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4). So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}. Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted with DSS as the software platform and the bandwidth control implemented by NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

First of all, we conduct some preliminary improvement experiments using only proportional part or integral part. Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP). Fig. \ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm. In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time. We can conclude that STP provides the best average quality level at the expense of high quality variance. This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation. In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality. Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.

Since STP and LTP have their own limitations, we implement the PID-based quality control algorithm, which can both reduces quality variance and improves average quality level. From the result shown in Fig. \ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP. An obvious proof can be found in Fig. \ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm. Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation. It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation. The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig. \ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.

@@

After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user. We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction. The result for the same test stream as used in subsection \ref{subsec:exp-control} is present in Fig. \ref{fig:fluctuation-psnr}. It shows PSNR change perceived by the user when available bandwidth fluctuates around certain values (600kbps, 800kbps, 1000kbps and 1200kbps). The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed. It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 450s in Fig. \ref{fig:Fluctuation-PSNR1} or around 250s in Fig. \ref{fig:Fluctuation-PSNR3}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 400s in Fig. \ref{fig:Fluctuation-PSNR2} or around time 500s in Fig. \ref{fig:Fluctuation-PSNR4}). The average and variance value of PSNR is also calculated and present in Fig. \ref{fig:fluctuation-psnr}, which showing clearly the proposed system's advantage. For instance, in Fig. \ref{fig:Fluctuation-PSNR4} where bandwidth fluctuates around 1200kbps, the average PSNR delivered by the proposed system is 41.14dB, 0.66dB higher than that of the baseline system, and the PSNR variance is also reduced from 0.63 to 0.21, indicating a more smooth video quality change.

@@

In this paper, we propose an adaptive video streaming system with optimized bitstream extraction and PID-based quality control. The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet. The priority values can then be stored in the bitstream and used for R-D optimized extraction. Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity. The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change. Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction. The SVC streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.

@@

>>>>

There are generally two options to enable adaptive video streaming. The first option is called simulcast, where several independent bitstreams, each with different video quality, are stored at the server, and the client selects one of them according to currently available bandwidth. Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option. The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, an extension of the H.264/AVC video coding standard \cite{SVCOverview}, which allows scalability of video bitrate and quality with only one single bitstream. In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs). These NALUs are separated into one base layer for basic video quality and multiple enhancement layers for video quality improvement. By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.

The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy. Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation. However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost. SVC streaming systems, on the contrary, do not have above shortcomings. Since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation. Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream. Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention \cite{Zhu2013}\cite{Dan2013}\cite{Yang2014}.

In the SVC adaptive video streaming system, there are two key problems that need to be addressed well. First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained. This is called the bitstream extraction problem. Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate. Second, when the bandwidth changes with time, it's necessary to make decisions about whether and how to adjust the bitrate or video quality. This problem is called quality control, which means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth. A good quality control algorithm should determine a suitable bitrate for current bandwidth condition, and keep the video quality both smooth and at a high level.

In this paper, an efficient adaptive video streaming system based on SVC is proposed with the above two problems better solved. Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the proposed system. The original DSS project is modified and SVC support is added to it, for the purpose of both research and application. Then novel algorithms for bitstream extraction and quality control are designed and implemented to achieve significant improvement in terms of user-perceived video quality. The contributions of our work can be summarized as follows:
\begin{itemize}
\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its R-D impact, thus enables optimized bitstream extraction.
\item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
\end{itemize}

@@

Bitstream extraction is the operation of choosing a subset of data packets from a whole SVC bitstream to form a sub-stream. It makes the bitrate adjustable and is the prerequisite of an adaptive streaming system. Fig. \ref{fig:Bitstream-Extraction} illustrates the structure of an SVC stream and a possible way to extract a sub-stream from it. The data packets in the stream are divided into different layers. The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames. The arrows on the top point from the referenced frame to the frame which is dependent on it. The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame. Data packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction. For example, the dash line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.

@@

For a typical ``0-1 Knapsack Problem", the optimal solution can generally be found using the dynamic programming algorithm. However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the stream's data packets. First, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included. For example, in Fig. \ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame. Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on other packets. Unless we discard a packet and calculate the distortion it causes for real, there is no way to exactly tell its value. In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem. All the effort is made to obtain a solution that is as good as possible.

@@

Quality control is the second problem we will address in this paper. The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user. In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed. Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

@@

The following of this paper will present our solution for each of the problems in detail. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.

@@

Consider a video bitstream with 8-frame GOPs shown in Fig. \ref{fig:GOP_Structure}. Base layer packets are colored black, and enhancement packets with the same color are allocated in one group. In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other. For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0). So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs. Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames. To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$. For the example in Fig. \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$. However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g. frame 0, 8, 16, etc.) packets. The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs. As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20). So key frame enhancement packets within the same quality layer (e.g. packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4). Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}. Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted with DSS as the software platform, and the bandwidth simulation is implemented with NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

First of all, we conduct some preliminary improvement experiments using only proportional part or integral part of the PID model. Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP). Fig. \ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm. In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time. We can conclude that STP provides the best average quality level at the expense of high quality variance. This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation. In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality. Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.

Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce quality variance and improve average quality level. From the result shown in Fig. \ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP. An obvious proof can be found in Fig. \ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm. Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation. It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation. The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig. \ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.

@@

After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user. We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction. The result for the same test stream as used in subsection \ref{subsec:exp-control} is present in Fig. \ref{fig:fluctuation-psnr}. It shows PSNR change perceived by the user when available bandwidth fluctuates around certain values (600kbps, 800kbps, 1000kbps and 1200kbps). The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed. It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 450s in Fig. \ref{fig:Fluctuation-PSNR1} or 250s in Fig. \ref{fig:Fluctuation-PSNR3}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 400s in Fig. \ref{fig:Fluctuation-PSNR2} or 500s in Fig. \ref{fig:Fluctuation-PSNR4}). The average and variance value of PSNR is also calculated and present in Fig. \ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage. For instance, in Fig. \ref{fig:Fluctuation-PSNR4} where bandwidth fluctuates around 1200kbps, the average PSNR delivered by the proposed system is 41.14dB, 0.66dB higher than that of the baseline system, and the PSNR variance is also reduced from 0.63 to 0.21, indicating a more smooth video quality change.

@@

In this paper, an adaptive video streaming system with optimized bitstream extraction and PID-based quality control is proposed. The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet. The priority values can then be stored in the bitstream and used for R-D optimized extraction. Experimental results show that the method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity. The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change. Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction. The proposed SVC adaptive streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.

@@

\bibitem{Zhu2013}
Z. Zhu, S. Li, and X. Chen, ``Design QoS-aware multi-path provisioning strategies for efficient cloud-assisted SVC video streaming to heterogeneous clients'', in {\em IEEE Transactions on Multimedia}, vol. 15, no. 4, pp.758-768, 2013.

\bibitem{Dan2013}
G. Dan, O. Hadar, R. Ohayon, and N. Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', in {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.588-589, 2013.

\bibitem{Yang2014}
E. Yang, Y. Ran, S. Chen, and J. Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.1323-1328, 2014.
